### 2012-07-30 docs/matching_algo/matching_algo.tex

\section{Inner Loop: Concrete Matching}
\label{sec:inner-loop}

@@

\section{Testing Wrapper: Concrete Matching Only}
\label{sec:test-wrapper}

For testing purposes, it is straight-forward to wrap the above procedure to just do concrete matching.  When we populate the match state, we do it in the following manner:
\begin{itemize}
\item $U_C$ will contain all circles
\item $U_W$ will contain all other wire vertices, except those forming bare wires (boundary vertices connected to another boundary vertex)
\item $U_N$ will contain all node vertices
\item $P$, $P_S$ and $m$ will be empty
\end{itemize}

@@

\section{Full Wrapper: Lazy !-Box Expansion}
\label{sec:full-wrapper}

This algorithm performs lazy $!$-box expansion to find all possible matchings of a pattern graph against a string graph.  In order for the algorithm to be deterministic, we disallow pattern graphs with empty $!$-boxes or $!$-boxes containing only bare wires, as these may be expanded any number of times and still match any graph that contains a wire.

@@

@@

We calculate the variant at the point where we consider terminating the loop, immediately after the concrete matching step.  If the previous iteration involved killing one or more $!$-boxes, $V_L\setminus\dom(m)$ will decrease (by the combined size of the $!$-boxes).  If the previous iteration involved expanding a $!$-box, $|\dom(m)|$ will increase (by the size of the $!$-box, excluding any bare wires).  $V_L\setminus\dom(m)$ is clearly bounded below by $0$, and $|\dom(m)|$ is bounded below by $|V_G|$, by global invariant \ref{enum:g-inv-inj}, so $n$ is bounded below by $0$ and decreases with every iteration.  Hence the algorithm terminates.

@@

\section{Improved Pattern Wrapper: Component-wise !-box Expansion}

@@

\section{Alternate Wrapper: Partial (Non-strict) Graph Matching}

>>>>

\section{Inner Loop: (Partial) Concrete Matching}
\label{sec:inner-loop}

@@

\section{String Graph to String Graph Matching}
\label{sec:test-wrapper}

For testing purposes, and as a general procedure for matching string-graphs against other string-graphs, it is straight-forward to wrap the above procedure to just do concrete matching.  When we populate the match state, we do it in the following manner:
\begin{itemize}
\item $U_C$ will contain all circles
\item $U_W$ will contain all other wire vertices, except those forming bare wires (boundary vertices connected to another boundary vertex)
\item $U_N$ will contain all node vertices
\item $P$, $P_S$ and $m$ will be empty
\end{itemize}

@@

\section{Greedy $!$-Graph to String Graph Matching}
\label{sec:full-wrapper}

This algorithm lazily expands or kills $!$-boxes to find all possible matchings of a pattern graph against a string graph, greedily matching everything not in a $!$-box at each stage.  The algorithm is complete and terminating only for those pattern graphs where no sequence of $!$-operations can result in a $!$-box that is empty or contains only bare wires (the implementation in Quantomatic actually allows such pattern graphs, but will fail to find all possible matchings for such graphs).

@@

The algorithm terminates, on the assumption that no sequence of $!$-box operations will ever produce a \textit{wild} $!$-box (ie: a $!$-box that is either empty or contains only bare wires), by the following argument.

@@

We calculate the variant at the point where we consider terminating the loop, immediately after the concrete matching step.  If the previous iteration involved killing one or more $!$-boxes, $V_L\setminus\dom(m)$ will decrease (by the combined size of the $!$-boxes, less bare wires --- this amount is positive due to the above assumption).  If the previous iteration involved expanding a $!$-box, $|\dom(m)|$ will increase (by the size of the $!$-box, excluding any bare wires).  $V_L\setminus\dom(m)$ is clearly bounded below by $0$, and $|\dom(m)|$ is bounded below by $|V_G|$, by global invariant \ref{enum:g-inv-inj}, so $n$ is bounded below by $0$ and decreases with every iteration.  Hence the algorithm terminates.

Note that Quantomatic's implementation ensures termination (at the expense of completeness) for all pattern graphs by killing any wild $!$-boxes as soon as they are produced.

@@

Note that Quantomatic's implementation is incomplete when the pattern graph is \textit{wild} --- ie, when there is a sequence of $!$-box operations on the pattern graph that can produce a wild $!$-box.

\section{Component-wise $!$-Graph to String Graph Matching}

@@

\section{Partial (Non-strict) String Graph to String Graph Matching}
